% Acknowledgement
% If relevant give a special thanks to the people who supported you during your thesis
% writing.

\pagestyle{empty}
\chapter*{Preface}

Embarking on this thesis has been a long and hard journey.
Juggling work and study simultaneously was no easy feat, and
it often felt like a balancing act that required all my focus and energy.
Despite the late nights and the constant juggle between professional and
academic obligations, the sense of accomplishment I feel now makes it all
worthwhile. The original work, findings and results are produced by the author,
including the initial the original text. The language of this work has been
modified (for purposes of grammar and phrasing) using
grammarly\cite{Grammarl47:online} and openai\cite{OpenAI35:online}.

I'm really thankful to my current employer for their help and for letting me study while
working. I am thankful to my director, Parvez
Shaik, and my manager, Kari Lee, for their mentorship and encouragement. Their
belief in my abilities and the support from the entire team have been a source
of inspiration and motivation.

I also owe a big thank you to my professors and mentors. Professor Sami Sainio
deserves a special mention for his valuable advice on thesis writing and his
thorough reviews of my drafts. His advice made my work much better. I'm also
very thankful to Professor Ville Jääskeläinen, who runs the IT Master's program,
and Dr. James Collins, for their help and guidance.

I also need to say a huge thank you to my family for always encouraging me
during all of my studies.

Espoo

Bhabani Sankar Das
% \DTMsetdatestyle{dMonthyyyy}
% \date{\today}

\clearpage

