\documentclass[12pt,a4paper,oneside,article]{memoir}%Do not touch this first line ;)

% Global information (title of your thesis, your name, degree programme, major, etc.)

\def\bilingual{no}%For Finnish students, you must have 2 abstracts, one in English and one in your native language (Finnish or Swedish), so "yes", your thesis is bilingual.
%\def\bilingual{no}%For international student writing in English, only one language and one abstract.

\def\thesislang{english} %change this depending on the main language of the thesis.
%\def\thesislang{english} % "english" is the only other supported language currently. If someone has the swedish, please contribute!

%\def\secondlang{english} %if the main language is Finnish (or Swedish), you must have 2 abstracts (one in Finnish (or Swedish) and one in English)
%\def\secondlang{finnish}
%If the main language is English and that you are native Finnish (or Swedish) speaker, you must have also abstract in your native language on top of the English one.

\author{Bhabani Sankar Das} %your first name and last name

%\def\alaotsikko{Alaotsikko/Subtitle} %DISABLED, seems not to be an option with the 2018 template. If you really need it, uncomment and modify style/title.tex accordingly.

%License
%When publishing your thesis to theseus.fi, you can keep all rights reserved to you,
%or use one of the Creative Commons https://creativecommons.org/licenses/?lang=en
%This attribute will set the license in the metadata of the generated pdf.
%possible options (case sensitive):
%all (keep all rights reserved to yourself)
%by (Attribution)
%by-sa (Attribution-ShareAlike)
%by-nd (Attribution-NoDerivs)
%by-nc (Attribution-NonCommercial)
%by-nc-sa (Attribution-NonCommercial-ShareAlike)
%by-nc-nd (Attribution-NonCommercial-NoDerivs)
%Note that theseus do not accept dedication to public domain CC0
\def\thesiscopy{all}

%Finnish section, for title/abstract
\def\otsikko{Opinnäytetyön otsikko}
\def\tutkinto{Tutkinto (esim. Insinööri (AMK))} % change to your needs, e.g. "YAMK", etc.
\def\kohjelma{Koulutusohjelma (esim. Tieto\textendash ja viestintätekniikka)}
\def\suuntautumis{Ammatillinen pääaine (esim. Mobile Solutions)}
\def\thesisfi{Insinöörityö}%was Opinnäytetyö
\def\ohjaajat{
Titteli Etunimi Sukunimi\newline
Titteli Etunimi Sukunimi
}
\def\tiivistelma{
Tämä on tiivistelmän ensimmäinen kappale. Tiivistelmän kappaleet loppuvat komentoon newline, jotta saadaan yksi tyhjä rivi aikaiseksi. \newline

Tämä on tiivistlemän toinen kappale.
}
\def\avainsanat{avainsana, avainsana}
\def\aihe{Lyhyt kuvaus opinnäytetyöstä. Max 255 merkkiä.}%for the pdf metadata/properties. If not used, empty it and also the \def\subject.

%English section, for title/abstract
\title{Effective Implementation and Evaluation of Fuzz Testing: A Comparative Study in an Embedded Software Company}
\def\metropoliadegree{Master of Engineering} % change to your needs, e.g. "master", etc.
\def\metropoliadegreeprogramme{Information Technology}
\def\metropoliaspecialisation{Networking and Services }
\def\thesisen{Master's Thesis} % change to your need, e.g. master's
\def\metropoliainstructors{
First name Last name, Title (e.g.: Project Manager)\newline
First name Last name, Title (Sami Sainio: Principal Lecturer)
}
\def\abstract{
In the era of pervasive digital interconnection, the robustness and security
resilience of embedded software systems are paramount. As these systems,
which are integral to various industries such as automotive, aviation, and
consumer electronics, grow more complex, they present an expanding
cybersecurity threat landscape. This thesis seeks to enhance the software testing
methods of a case company's embedded software systems through fuzz testing, an automated,
a technique that exposes vulnerabilities by inputting invalid or unexpected data.

%\hspace{2cm}
\hspace{0.5cm}The motivation for this study is rooted in the growing necessity for stronger
security measures within embedded systems due to escalating cybersecurity
threats. A significant challenge lies in selecting a suitable fuzzing tool
from the multitude of options available. To address this issue, this study
takes a practical, hands-on approach by being conducted within the
unique environment of a case-in company.

\hspace{0.5cm}After an exhaustive literature review of various fuzzing tools,
two popular tools, American Fuzzy Lop (AFL++) and LibFuzzer, are
selected for an in-depth comparative analysis. These tools are chosen
based on their reputation, widespread use, and supportive literature evidence.
The study examines pivotal factors like integration ease, efficiency, speed,
code coverage, and the identification of vulnerabilities, providing an
impartial perspective to aid the decision-making process.

\hspace{0.5cm}In conclusion, the practical assessment of this study will yield crucial
insights into the relative performance of AFL++ and LibFuzzer within the case
company's unique environment. Based on these insights and the outcomes of the
comparative analysis, the optimal fuzzing tool will be recommended. The ultimate
promise of this thesis is to deliver a robust, evidence-based strategy for
enhancing the security resilience of the case company's embedded software
systems through tailored fuzz testing.

}
\def\metropoliakeywords{fuzzing, embedded system, AFL++, libFuzzer}
\def\subject{short description of the thesis. Max 255 characters.}%for the pdf metadata/properties. If not used, empty it and also the \def\aihe.
